[Artifact57] Robust Resource Bounds with\\ Static Analysis and Bayesian Inference

### 2024-03-11 README/getting_started_guide.tex
Added a warning that macOS may change the name of the Docker image after loading

Load and run the Docker image as follows:
\begin{verbatim}
$ docker load --input hybrid_aara.tar.gz
$ docker run --name hybrid_aara -it --rm hybrid_aara
root@fca41f6f696d:/home/hybrid_aara/benchmark_suite/playground#
\end{verbatim}
%
It creates a Docker conainer (i.e., a runnable instance of the Docker image) and
starts a shell inside the container.
%
Throughout this document, any command line starting with \texttt{\#} is executed
inside the Docker container, and any command line starting with \texttt{\$} is
executed in your local machine's terminal.

@@

Hybrid RaML's executable is the file \texttt{/home/hybrid\_aara/raml/main}.
%
Its location has already been added to the \texttt{PATH} variable so that we can
call Hybrid RaML by running \texttt{main} anywhere in the Docker container's
filesystem.
%
Hybrid AARA (and its implementation Hybrid RaML) provides three modes of hybrid
resource analysis: Hybrid \Opt{}, Hybrid \BayesWC{}, and Hybrid \BayesPC{}.
%
Although the paper also describes purely data-driven resource analysis, which is
a special case of hybrid resource analysis, this Getting Started Guide focuses
on hybrid resource analysis of the function \texttt{append}.

>>>>

Load a Docker image by running
\begin{verbatim}
$ docker load --input hybrid_aara.tar.gz
\end{verbatim}
%
It creates an image named \texttt{hybrid\_aara} and stores it locally on your
machine.
%
On some platforms (e.g., macOS), Docker may create an image with a slightly
different name from \texttt{hybrid\_aara}.
%
You can check the name of the image by running \verb|$ docker ps|, which will
display a list of images on your local machine.

To run the image \texttt{hybrid\_aara}, run
\begin{verbatim}
$ docker run --name hybrid_aara -it --rm hybrid_aara
root@fca41f6f696d:/home/hybrid_aara/benchmark_suite/playground#
\end{verbatim}
%
It creates a Docker container (i.e., a runnable instance of the Docker image)
named \texttt{hybrid\_aara} and starts a shell inside the container.

Throughout this document, any command line starting with \texttt{\#} is executed
inside the Docker container, and any command line starting with \texttt{\$} is
executed in your local machine's terminal.

@@

Hybrid RaML's executable is the file \texttt{/home/hybrid\_aara/raml/main}.
%
Its location has already been added to the \texttt{PATH} variable so that we can
call Hybrid RaML by running \texttt{main} anywhere in the Docker container's
filesystem.
%
Hybrid AARA (and its implementation Hybrid RaML) provides three modes of hybrid
resource analysis: Hybrid \Opt{}, Hybrid \BayesWC{}, and Hybrid \BayesPC{}.
%
Although the paper also describes purely data-driven resource analysis
(Section~5), which is a special case of hybrid resource analysis, this Getting
Started Guide focuses on hybrid resource analysis of the function
\texttt{append}.

### 2024-03-11 README/step_by_step_instructions.tex
Added a warning that macOS may change the name of the Docker image after loading

To view the updated tables and plots of the new experimental results, follow the
steps in \cref{sec:display experiment results}.
%
The experimental results for (Data-Driven and Hybrid) \BayesWC{} and \BayesPC{}
after rerunning the experiments may look different from the tables and plots
reported in the updated version of the paper.
%
This is because \BayesWC{} and \BayesPC{} run sampling-based Bayesian inference
algorithms that are stochastic.
%
Nonetheless, there should not be any significant deviation.

@@

The project directory contains two additional directories.
%
The third-party C++ library volesti\footnote{Available here:
\url{https://github.com/GeomScale/volesti}.} is stored in the directory
\texttt{volesti}.
%
The linear-program solver COIN-OR CLP\footnote{Available here:
\url{https://github.com/coin-or/Clp}.} is stored in the directory \texttt{clp}.

The code for building a Docker image is publicly available on GitHub:
\url{https://github.com/LongPham7/hybrid_aara_artifact}.
%
To build a Docker image, clone the GitHub repository and then run (in the root
directory)
\begin{verbatim}
$ docker build -t hybrid_aara .
\end{verbatim}
%
It will take 20--30 minutes.
%
The resulting image is named \texttt{hybrid\_aara} and is stored locally on your
machine.
%
To run this image after it is built, run
\begin{verbatim}
$ docker run --name hybrid_aara -it --rm hybrid_aara
\end{verbatim}
%
If you want to save the image as a tar archive and compress it, run
\begin{verbatim}
$ docker save hybrid_aara | gzip > hybrid_aara.tar.gz
\end{verbatim}

>>>>

To view the updated tables and plots of the new experimental results, follow the
steps in \cref{sec:display experiment results}.
%
The experimental results for (Data-Driven and Hybrid) \BayesWC{} and \BayesPC{}
after rerunning the experiments may look different from the tables and plots
reported in the updated version of the paper.
%
This is because \BayesWC{} and \BayesPC{} run sampling-based Bayesian inference
algorithms that are stochastic.
%
Nonetheless, there should not be any significant deviation from the results
reported in the paper.

@@

The project directory contains two additional directories that come from other
sources.
%
The third-party C++ library volesti\footnote{Available here:
  \url{https://github.com/GeomScale/volesti}.} is stored in the directory
\texttt{volesti}.
%
The linear-program solver COIN-OR CLP\footnote{Available here:
  \url{https://github.com/coin-or/Clp}.} is stored in the directory \texttt{clp}.

The code for building a Docker image is available on GitHub:
\url{https://github.com/LongPham7/hybrid_aara_artifact}.
%
To build a Docker image, clone the GitHub repository and then run (in the root
directory)
\begin{verbatim}
$ docker build -t hybrid_aara .
\end{verbatim}
%
We need a period at the end of the command to indciate that Dockerfile exists in
the current working directory.
%
The build will take 20--30 minutes.
%
The resulting image is named \texttt{hybrid\_aara} and is stored locally on your
machine.

To run the image \texttt{hybrid\_aara}, run
\begin{verbatim}
$ docker run --name hybrid_aara -it --rm hybrid_aara
\end{verbatim}
%
If you want to save the image as a tar archive and compress it, run
\begin{verbatim}
$ docker save hybrid_aara | gzip > hybrid_aara.tar.gz
\end{verbatim}
